Arrows for Parallel Computations

### 2017-11-29 paper/content/benchmarks.tex
boldfacing in table

\subsection{Benchmark results}

The difference between, say, PArrows with \ensuremath{\Conid{Par}} Monad backend and a
genuine \ensuremath{\Conid{Par}}
Monad benchmark is very small. To give an example, it is $0.4\seconds$ in favour of PArrows for 16 cores ($10.8\seconds$ vs. $11.2\seconds$) and $-0.8\seconds$ in favour of the \ensuremath{\Conid{Par}} monad for 8 cores ($16.1\seconds$ vs. $16.9\seconds$) for
the Sudoku benchmark in the shared memory setting. It is almost invisible in speedup and
(non shown) run time plots. We thus show only the results for the
PArrows-enabled versions in the backend-comparison.

To show that PArrows induce very small overhead even in a distributed context (and in general as well), we compare the original Eden
versions of the benchmark to its PArrows-enabled counterpart in the \rmtest, \torustest and \jacobitest benchmarks. We plot execution time differences between measurements for
PArrows and the corresponding backend in a separate plot
(Figs.~\ref{fig:bench-rm-dist}--\ref{fig:torusBenchmark}). As an example, the differences range in
about $0.5\seconds$ for the execution time of $46\seconds$ on 256 cores
for distributed \rmtest with PArrows and Eden. For these comparisons, the plots show absolute
time differences that are not relative \wrt the total execution time.
Furthermore, the error bars ends were computed from point-wise maximum of both standard
deviations from both measurements for PArrows and non-PArrows
versions. These are the values provided by the \ensuremath{\Varid{bench}} package that we
used for bench-marking. We call a difference between two versions
significant when the border of the error bar of absolute time
difference is above or below zero. In other words: the time
difference is significant if it is outside of the measurement error.

@@

\newcommand{\performanceSkelRMDistDiff}[5]{
\performancediffplot{Run time differences\\for \rmtest \enquote{#1 #2}}{(Eden $-$ PArrows)}{256}{#3}{
\addplot+[mark=*,very thick,error bars/.cd,
    y dir=both,y explicit] table [x="nCores", y="time", y error="max stddev", col sep=comma, mark=dots,
smooth]{benchmarks/distributed-rm/#1-#2-diff.csv};
}{#4}{#5}{\plotwidthDist}
}

@@

\newcommand{\performanceJacobiDistDiff}[5]{
\performancediffplot{Run time differences\\for \jacobitest \enquote{#2}}{(Eden $-$ PArrows) #2}{256}{#3}{
\addplot+[mark=*,very thick,error bars/.cd,
    y dir=both,y explicit] table [x="nCores", y="time", y error="max stddev", col sep=comma, mark=dots,
smooth]{benchmarks/distributed-jacobi/#1-#2-diff.csv};
}{#4}{#5}{\plotwidthDist}
}

@@

\newcommand{\performanceTorusDistDiff}[4]{
\performancediffplot{Run time differences\\for \torustest \enquote{#1}}{(Eden $-$ PArrows)}{256}{#2}{
\addplot+[mark=*,very thick,error bars/.cd,
    y dir=both,y explicit] table [x="nCores", y="time", y error="max stddev", col sep=comma, mark=dots,
smooth]{benchmarks/distributed-torus/#1-diff.csv};
}{#3}{#4}{\plotwidthDist}
}

>>>>

\subsection{Benchmark results}
To show that PArrows induce very small overhead even in a distributed context (and in general as well), we compare the original Eden
versions of the benchmark to its PArrows-enabled counterpart in the \rmtest, \torustest and \jacobitest benchmarks. We plot execution time differences between measurements for
PArrows and the corresponding backend in a separate plot
(Figs.~\ref{fig:bench-rm-dist}--\ref{fig:torusBenchmark}). As an example, the differences range in
about $0.5\seconds$ for the execution time of $46\seconds$ on 256 cores
for distributed \rmtest with PArrows and Eden. For these comparisons, the plots show absolute
time differences that are not relative \wrt the total execution time.
Furthermore, the error bars ends were computed from point-wise maximum of both standard
deviations from both measurements for PArrows and non-PArrows
versions. These are the values provided by the \ensuremath{\Varid{bench}} package that we
used for benchmarking. We call a difference between two versions
significant when the border of the error bar of absolute time
difference is above or below zero. In other words: the time
difference is significant if it is outside of the measurement error.

@@

\newcommand{\performanceSkelRMDistDiff}[5]{
\performancediffplot{Overhead\\for \rmtest \enquote{#1 #2}}{(Eden $-$ PArrows)}{256}{#3}{
\addplot+[mark=*,very thick,error bars/.cd,
    y dir=both,y explicit] table [x="nCores", y="overhead", y error="stdDevForOverhead", col sep=comma, mark=dots,
smooth]{benchmarks/distributed-rm/#1-#2-diff.csv};
}{#4}{#5}{\plotwidthDist}
}

@@

\newcommand{\performanceJacobiDistDiff}[5]{
\performancediffplot{Overhead\\for \jacobitest \enquote{#2}}{(Eden $-$ PArrows) #2}{256}{#3}{
\addplot+[mark=*,very thick,error bars/.cd,
    y dir=both,y explicit] table [x="nCores", y="overhead", y error="stdDevForOverhead", col sep=comma, mark=dots,
smooth]{benchmarks/distributed-jacobi/#1-#2-diff.csv};
}{#4}{#5}{\plotwidthDist}
}

@@

\newcommand{\performanceTorusDistDiff}[4]{
\performancediffplot{Overhead\\for \torustest \enquote{#1}}{(Eden $-$ PArrows)}{256}{#2}{
\addplot+[mark=*,very thick,error bars/.cd,
    y dir=both,y explicit] table [x="nCores", y="overhead", y error="stdDevForOverhead", col sep=comma, mark=dots,
smooth]{benchmarks/distributed-torus/#1-diff.csv};
}{#3}{#4}{\plotwidthDist}
}
